What the hell is the title of this paper?

### 2018-05-14 NIPS 2018/main.tex
Updated up to RW

\begin{restatable}{theorem}{thmmv} \label{th:mmv}
Let $V$ be the fixed-point of the optimal Bellman operator $T$, and $Q$ the corresponding action-value function. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}). Let $\nu$ be a probability measure over the state-space. Then, for any $p \geq 1$:
\begin{equation}
\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{(1-\gamma)^2}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

\begin{restatable}{theorem}{thmm} \label{th:mm}
Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}). Let $\nu$ be a probability measure over the state-action space. Then, for any $p \geq 1$:
\begin{equation}
\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

@@

Our approach is mostly related to \cite{}. Although we both assume the tasks to share similarities in their value functions, \cite{} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian. On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators. Furthermore, \cite{} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation of Sec. \ref{sec:mgvt} and proves again the importance of capturing more complicated task distributions. 
Another related approach is \cite{}, where the authors propose a hierarchical Bayesian model for the distribution over tasks. Differently from our approach and \cite{}, they consider a distribution over transition probabilities and rewards, rather than value functions. In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it, thus providing efficient exploration via the transferred knowledge. However, \cite{} consider only finite MDPs, which poses a severe limitation in the algorithm's applicability. On the contrary, our approach can handle high dimensional tasks by allowing powerful function approximators. \todo{Cite also HIP}

\todo[inline]{Should we add more here or just leave a quick citation in the introduction?}

The idea of exploration via value function randomization we build upon was first proposed in the RL community by \cite{}. The authors extend the well-known LSTD \cite{} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a Thompson sampling-like procedure. Such approach was recently extended by \cite{}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems. Both these algorithms rely on the Gaussian assumption and, since they work in plain RL settings, have no informative prior available. On the other hand, our variational approximation allows more complex distributions (e.g., mixtures) to be adopted, while knowledge from the source tasks allows us to learn very informative priors. Finally, the variational approximation technique we consider in this work has been previously adopted in \cite{} to approximate an intractable posterior over the transition dynamics, which is then used to drive efficient exploration via an information-maximizing procedure.

>>>>

\begin{restatable}{theorem}{thmmv} \label{th:mmv}
Let $V$ be the fixed-point of the optimal Bellman operator $T$, and $Q$ the corresponding action-value function. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). Let $\nu$ be a probability measure over the state-space. Then, for any $p \geq 1$:
\begin{equation}
\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{(1-\gamma)^2}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

\begin{restatable}{theorem}{thmm} \label{th:mm}
Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). Let $\nu$ be a probability measure over the state-action space. Then, for any $p \geq 1$:
\begin{equation}
\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

@@

Our approach is mostly related to \cite{lazaric2010bayesian}. Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian. On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators. Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves again the importance of capturing more complicated task distributions. In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over tasks. Differently from our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions. In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it. However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability. On the contrary, our approach can handle high-dimensional tasks. In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks. This approach was recently extended in \cite{killian2017robust}, where the authors replace GPs with Bayesian neural networks to obtain a more scalable approach.\todo{More comments about HiP-MDPs? Should we discuss more related works?}

In the RL community, our approach is related to value function randomization\cite{osband2014generalization}. The authors extend the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling. Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems. Both these algorithms rely on the Gaussian assumption and, since they work in plain RL settings, have no informative prior available. On the other hand, our variational approximation allows more complex distributions (e.g., mixtures) to be adopted, while knowledge from the source tasks allows us to learn very informative priors.
